Democracy, Public Support, and Measurement Uncertainty

### 2021-05-05 paper/dcpo_demsupport.Rmd
dcpo uncertain done

load(here::here("data", "claassen_replication_input.rda"))
load(here::here("data", "claassen_m5_theta.rda"))
load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_theta.rda"))
load(here::here("data", "dcpo_sigma.rda"))
load(here::here("data", "dem_mood_apsr.RData"))

@@

```{r claassenUncertaintyAJPS}
claassen_replication <- readRDS("../data/claassen_replication.rds") %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)

ls_country <- unique(claassen_replication$country)
first_year <- min(claassen_replication$year)

@@

```{r claassenAPSR, eval = TRUE}

sd.plm <- pdata.frame(x, index = c("Country", "Year"))

ls_mods <- vector(mode = "list")

ls_mods[["ECM1.1"]] <- plm(
  diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
  data = sd.plm,
  model = "pooling"
)

ls_mods[["ECM1.2"]] <- plm(
  diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)
  + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1),
  data = sd.plm,
  model = "pooling"
)

ls_mods[["FD1.1"]] <-
  plm(
    SupDem_trim ~ Libdem_z + lnGDP_imp,
    model = "fd",
    data = sd.plm,
    index = "Country"
  )

ls_mods[["FD1.2"]] <-
  plm(
    SupDem_trim ~ Libdem_z + lnGDP_imp + Corrup_TI_z,
    model = "fd",
    data = sd.plm,
    index = "Country"
  )

ls_mods[["ECM2.1"]] <-
  plm(
    diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Polyarchy_z, lag = 1)
    + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)
    + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
    sd.plm,
    model = "pooling"
  )
ls_mods[["ECM2.2"]] <-
  plm(
    diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Polyarchy_z, lag = 1)
    + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)
    + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1) + diff(Corrup_TI_z, lag = 1)
    + plm::lag(Corrup_TI_z, 1),
    sd.plm,
    model = "pooling"
  )

# FD models

ls_mods[["FD2.1"]] <-
  plm(
    SupDem_trim ~ Polyarchy_z + Liberal_z + lnGDP_imp,
    model = "fd",
    data = sd.plm,
    index = "Country"
  )
ls_mods[["FD2.2"]] <-
  plm(
    SupDem_trim ~ Polyarchy_z + Liberal_z + lnGDP_imp + Corrup_TI_z,
    model = "fd",
    data = sd.plm,
    index = "Country"
  )

df_result_clsAPSR <- map(ls_mods, function(aMod){
  tidy(aMod, conf.int = TRUE) %>%
    mutate(std.error = vcovHC_se(aMod))
})

#save(df_result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
```

```{r claassenAPSRUncertainty}
ls_country <- unique(claassen_replication_input$data$country)
first_year <- min(claassen_replication_input$data$year)

@@

estimate_cls <- vector(mode = "list")

estimate_cls[[1]] <- function(aDataset) {
  plm(
      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Libdem_z, lag = 1)
  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
      model = "pooling",
      data = aDataset
    )
}

estimate_cls[[2]] <- function(aDataset) {
  plm(
      diff(theta, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)
  + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1),
      model = "pooling",
      data = aDataset
    )
}

df_result_clsUncertainAPSR <- map(estimate_cls, function(aModel){
  aFit <- map(df_clsAPSR, aModel)

  result_vars_cls_1k <- mitools::MIextract(aFit, fun = vcovHC_se)
  result_betas_cls_1k <- mitools::MIextract(aFit, fun = coef)

  summary(
      mitools::MIcombine(results = result_betas_cls_1k, 
                         variance = result_vars_cls_1k)
    ) %>% rownames_to_column(var = "term") %>%
    rename(conf.low = `(lower`,
           conf.high = `upper)`,
           estimate = results) %>%
    filter(!str_detect(term, "(Intercept)"))

save(df_result_clsUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))
```

@@

mods <- vector(mode = "list")
mods[[1]] <-
  plm(
    diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1)
    + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1),
    data = df_dcpoMeanAPSR,
    model = "pooling"
  )

mods[[2]] <-
  plm(
    diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1),
    data = df_dcpoMeanAPSR,
    model = "pooling"
  )

df_result_dcpoMeanAPSR <- map(mods, function(aMod) {
  aMod %>% 
    tidy %>%
    mutate(std.error = vcovHC_se(aMod),
           n = nobs(aMod`))
})

save(df_result_dcpoMeanAPSR, file = here::here("output", "estimates_dcpoMeanAPSR.RDS"))
```

```{r dcpoUncertaintyAPSR}
df_dcpo <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>%
    left_join(df_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

estimate_dcpo <- vector(mode = "list")

estimate_dcpo[[1]] <- function(aDataset) {
  plm(
      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1)
      + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1),
      model = "pooling",
      data = aDataset
    )
}

estimate_dcpo[[2]] <- function(aDataset) {
  plm(
      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1),
      model = "pooling",
      data = aDataset
    )
}

df_result_dcpoAPSR <- map(estimate_dcpo, function(aModel){
  aFit <- map(df_dcpo, aModel)

  result_vars_dcpo_1k <- mitools::MIextract(aFit, fun = vcovHC_se)
  result_betas_dcpo_1k <- mitools::MIextract(aFit, fun = coef)

  summary(
      mitools::MIcombine(results = result_betas_dcpo_1k, 
                         variance = result_vars_dcpo_1k)
    ) %>% rownames_to_column(var = "term") %>%
    rename(conf.low = `(lower`,
           conf.high = `upper)`,
           estimate = results) %>%
    filter(!str_detect(term, "(Intercept)"))

save(df_result_dcpoAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
```

>>>>

claassen_replication <- readRDS("../data/claassen_replication.rds") %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)

load(here::here("data", "claassen_m5_theta.rda"))
load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_theta.rda"))
load(here::here("data", "dcpo_sigma.rda"))
load(here::here("data", "dem_mood_apsr.RData"))

@@

```{r claassenUncertaintyAJPS}
ls_country <- unique(claassen_replication$country)
first_year <- min(claassen_replication$year)

@@

```{r claassenAPSR, eval = TRUE}
load(here::here("data", "dem_mood_apsr.RData"))
sd.plm <- pdata.frame(x, index = c("Country", "Year"))

ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")

ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
  outer(ls_ctrlECM, paste0) %>% 
  as.vector()

ls_ivFD <- c("Libdem_z",
             "Polyarchy_z + Liberal_z")

ls_ctrlFD <- c("", " + Corrup_TI_z")

ls_eqFD <- glue("SupDem_trim ~ {ls_ivFD} + lnGDP_imp") %>% 
  outer(ls_ctrlFD, paste0) %>% 
  as.vector()

ls_mod <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = sd.plm)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'Country', data = sd.plm)")
)

df_result_clsAPSR <- map(ls_mod, function(mod) {
  result <- eval(parse(text = mod))
})

result_clsAPSR <- map(df_result_clsAPSR, function(aResult) {
  tidy_result <- tidy(aResult, conf.int = TRUE) %>% 
    mutate(std.error = vcovHC_se(aResult))

  glance_result <- glance.plm(aResult)

  ls_result <- list(tidy_result, glance_result)
})

names(result_clsAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", 
                           "fd1", "fd-regime1", "fd2", "fd-regime2")

#save(result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
```

```{r claassenAPSRUncertainty}
ls_country <- unique(claassen_replication$country)
first_year <- min(claassen_replication$year)

@@

ls_ivECM <- c("diff(Libdem_z, lag = 1) + plm::lag(Libdem_z, 1)", 
              "diff(Polyarchy_z, lag = 1) + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)")
ls_ctrlECM <- c("", " + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1)")

ls_eqECM <- glue("diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
  outer(ls_ctrlECM, paste0) %>% 
  as.vector()

ls_ivFD <- c("Libdem_z",
             "Polyarchy_z + Liberal_z")

ls_ctrlFD <- c("", " + Corrup_TI_z")

ls_eqFD <- glue("diff(theta, lag = 1) ~ {ls_ivFD} + lnGDP_imp") %>% 
  outer(ls_ctrlFD, paste0) %>% 
  as.vector()

ls_mod <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'Country', data = aData)")
)

result_clsUncertainAPSR <- map(ls_mod, function(aMod){ # reading a model
  result <- map(df_clsAPSR, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

  result_vars <- mitools::MIextract(result, fun = vcovHC_se)

  tidy_clsUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
                             variance = result_vars)) %>% 
    rownames_to_column(var = "term") %>%
        rename(conf.low = `(lower`,
               conf.high = `upper)`,
               estimate = results) %>%
        filter(!str_detect(term, "(Intercept)"))

  glance_clsUncertainAPSR <- glance.plm(result[[1]])

  result_clsUncertainAPSR <- list(tidy_clsUncertainAPSR, glance_clsUncertainAPSR)
})

names(result_clsUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")

save(result_clsUncertainAPSR, file = here::here("output", "estimates_clsAPSR.RDS"))

@@

ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
              "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")

ls_eqECM <- glue("diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + {ls_ivECM} + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1)") %>% 
  outer(ls_ctrlECM, paste0) %>% 
  as.vector()

ls_ivFD <- c("Vdem_libdem_z",
             "Vdem_polyarchy_z + Vdem_liberal_z")

ls_ctrlFD <- c("", " + corruption_z")

ls_eqFD <- glue("theta ~ {ls_ivFD} + lg_imp_mdpgdp") %>% 
  outer(ls_ctrlFD, paste0) %>% 
  as.vector()

ls_mod <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = df_dcpoMeanAPSR)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = df_dcpoMeanAPSR)")
)

df_result_dcpoMeanAPSR <- map(ls_mod, function(mod) {
  result <- eval(parse(text = mod))
})

result_dcpoMeanAPSR <- map(df_result_dcpoMeanAPSR, function(aResult) {
  tidy_result <- tidy(aResult, conf.int = TRUE) %>% 
    mutate(std.error = vcovHC_se(aResult))

  glance_result <- glance.plm(aResult)

  ls_result <- list(tidy_result, glance_result)
})

names(result_dcpoMeanAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")

save(result_dcpoMeanAPSR, file = here::here("output", "estimates_dcpoMeanAPSR.RDS"))
```

```{r dcpoUncertaintyAPSR}
ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

df_dcpoUncertainAPSR <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>%
    left_join(df_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

## The same as in the previous chunk

ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
              "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")

ls_eqECM <- glue("diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + {ls_ivECM} + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1)") %>% 
  outer(ls_ctrlECM, paste0) %>% 
  as.vector()

ls_ivFD <- c("Vdem_libdem_z",
             "Vdem_polyarchy_z + Vdem_liberal_z")

ls_ctrlFD <- c("", " + corruption_z")

ls_eqFD <- glue("theta ~ {ls_ivFD} + lg_imp_mdpgdp") %>% 
  outer(ls_ctrlFD, paste0) %>% 
  as.vector()

### Different datasets

ls_mod <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = df_dcpoUncertainAPSR)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = df_dcpoUncertainAPSR)")
)

result_dcpoUncertainAPSR <- map(ls_mod, function(aMod){ # reading a model
  result <- map(df_dcpoUncertainAPSR, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

  result_vars <- mitools::MIextract(result, fun = vcovHC_se)

  tidy_dcpoUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
                             variance = result_vars)) %>% 
    rownames_to_column(var = "term") %>%
        rename(conf.low = `(lower`,
               conf.high = `upper)`,
               estimate = results) %>%
        filter(!str_detect(term, "(Intercept)"))

  glance_dcpoUncertainAPSR <- glance.plm(result[[1]])

  result_dcpoUncertainAPSR <- list(tidy_dcpoUncertainAPSR, glance_dcpoUncertainAPSR)
})

names(result_dcpoUncertainAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")

save(result_dcpoUncertainAPSR, file = here::here("output", "estimates_dcpoAPSR.RDS"))
```
